---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("stats 220(Responses) - Form responses 1.csv")

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    score = Score,
    hours_on_instagram = `How many hours do you spend on Instagram?`,
    post_type = `What type of post do you see the most?`,
    interaction = `How do you normally interact with a post you like`
  )

mean_hours <- latest_data %>%
  summarise(mean_hours = mean(hours_on_instagram, na.rm = TRUE)) %>%
  pull(mean_hours)

top_post <- latest_data %>%
  count(post_type, sort = TRUE) %>%
  slice(1) %>%
  pull(post_type)

top_interaction <- latest_data %>%
  count(interaction, sort = TRUE) %>%
  slice(1) %>%
  pull(interaction)

```

```{css}
body {
  background-color: #f7f9fc;
  font-family: Arial, sans-serif;
  color: #333333;
  padding: 20px;
}

h2 {
  color: #1f4e79;
  border-bottom: 3px solid #1f4e79;
  padding-bottom: 5px;
}

p {
  font-size: 18px;
  line-height: 1.6;
}

img {
  border-radius: 10px;
}

```


```{r}
ggplot(latest_data, aes(x = post_type)) +
  geom_bar(fill = "steelblue") +
  labs(
    title = "Most Common Types of Instagram Posts Seen",
    x = "Post type",
    y = "Count"
  ) +
  theme_minimal()
```

```{r}
ggplot(latest_data, aes(x = interaction)) +
  geom_bar(fill = "darkorange") +
  labs(
    title = "How People Usually Interact With Posts They Like",
    x = "Interaction type",
    y = "Count"
  ) +
  theme_minimal()
```


## Introduction

The focus of my data collection for this project was Instagram use and user behaviour. Over a period of time, I collected observational data about how many hours respondents spent on Instagram, what type of post they saw the most, and how they normally interacted with posts they liked. This allowed me to build a small tidy dataset with both numeric and categorical variables, which made it suitable for summary statistics and visual analysis.

One important guideline for designing forms is that the questions should be clear, relevant, and easy for respondents to answer. I considered this by keeping my form short and focused on only a few variables that directly matched the purpose of the project. I included one numeric question using short answer with response validation for the number of hours spent on Instagram, and categorical multiple choice questions for the type of post most often seen and how respondents usually interacted with posts they liked. I also made sure the responses were anonymous, which was appropriate because the form was about personal social media habits.

The data collected can be used to learn something meaningful because it allows comparisons between common post types, interaction habits, and time spent on Instagram. For example, I can identify which type of content is most commonly seen and what type of interaction is most common overall.

Google Form link:  
<https://docs.google.com/forms/d/e/1FAIpQLSeoLCVKR3NLUnAU6LJpVekNu1rHofKE_9YMxyzHXu4HzMHCzQ/viewform?usp=dialog>

Form design and data collection for this project were completed by me.

## Dynamic report

Here is the link to my GitHub Pages published dynamic report:

[Paste your GitHub Pages dynamic report link here]

## Creativity

I demonstrated creativity in this project by choosing Instagram use and interaction as the focus of the observational logging. While the project instructions gave examples of possible topics, I selected a topic that was relevant to daily online behaviour and allowed for both numeric and categorical analysis. I also improved the presentation of the dynamic report by adding custom CSS styling so that the final report was clearer and more visually appealing. In addition, I made sure the bar charts were informative and directly connected to the context of the data, rather than simply producing generic graphs. These choices made the report more meaningful and engaging.

## Learning reflection

One important idea I learned from Module 2 is that dynamic reporting systems make it possible to connect data, code, and communication together in one workflow. Instead of manually updating results every time the data changes, a dynamic report can automatically update summary values and graphs when new observations are added. This makes reporting much more efficient and also reduces the chance of mistakes caused by copying results by hand.

This project also made me more curious about how data technologies can be used to build interactive online reports and dashboards. I would like to explore more about how web-based reporting tools can be used to present live or regularly updated data in more engaging ways. Since I completed the project individually, one other way I can continue to develop my group work skills is by taking a more active role in future team assignments and practising clearer communication when dividing tasks and sharing progress.

```
## Appendix

```{r file='exploration.R', eval=FALSE, echo=TRUE}

---

