---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSkcOHoppSOvVVghmTusa3hVYpM_62Niikohv6mT3-JrJL-jEE-rcmcGmbHc_dXOaL8aczNgJOx1ve9/pub?output=csv"

logged_data <- read_csv(csv_url)

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    score = Score,
    hours_on_instagram = `How many hours do you spend on Instagram?`,
    post_type = `What type of post do you see the most?`,
    interaction = `How do you normally interact with a post you like`
  )

mean_hours <- latest_data %>%
  summarise(mean_hours = mean(hours_on_instagram, na.rm = TRUE)) %>%
  pull(mean_hours)

top_post <- latest_data %>%
  count(post_type, sort = TRUE) %>%
  slice(1) %>%
  pull(post_type)

top_interaction <- latest_data %>%
  count(interaction, sort = TRUE) %>%
  slice(1) %>%
  pull(interaction)
```

```{css}
body {
  background-color: #f7f9fc;
  font-family: Arial, sans-serif;
  color: #333333;
  padding: 20px;
}

h2 {
  color: #1f4e79;
  border-bottom: 3px solid #1f4e79;
  padding-bottom: 5px;
}

p {
  font-size: 18px;
  line-height: 1.6;
}

img {
  border-radius: 10px;
}

```
## Instagram observational logging report

This report summarises patterns in Instagram use and interaction based on the data collected through my Google Form.

On average, respondents spent **`r round(mean_hours, 2)` hours** on Instagram.

The most common type of post seen was **`r top_post`**.

The most common way respondents interacted with a post they liked was **`r top_interaction`**.

```{r}
ggplot(latest_data, aes(x = post_type)) +
  geom_bar(fill = "steelblue") +
  labs(
    title = "Most Common Types of Instagram Posts Seen",
    x = "Post type",
    y = "Count"
  ) +
  theme_minimal()
```

```{r}
ggplot(latest_data, aes(x = interaction)) +
  geom_bar(fill = "darkorange") +
  labs(
    title = "How People Usually Interact With Posts They Like",
    x = "Interaction type",
    y = "Count"
  ) +
  theme_minimal()
```

